### 2020-04-26 document/paper.tex

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\makeatletter
\newcommand{\printfnsymbol}[1]{%
  \textsuperscript{\@fnsymbol{#1}}%
}
\makeatother

\begin{document}
%
\title{Wireframe2DOM: From Static Graph to Responsive HTML}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Shangyin Tan\thanks{equal contribution} \and
Tiger Tang\printfnsymbol{1}}
%
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Purdue University\\
\email{\{tan279,tang426\}@purdue.edu}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Program Synthesis  \and Web Development \and User Interface}
\end{abstract}
%
%
%
\section{Introduction}
\section{Background}
\section{Related work}
\section{Illustrative example}
\section{Formal problem definition}
\section{Algorithm}
First we divide the rectangles into section based on their $y$-axis. Then we use
greedy to find the earlist possible cut $y$ such that this $y$ does not divide any
other rects.
\section{Evaluation}
\section{Conclusion}

%\subsection{A Subsection Sample}

% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.

% Subsequent paragraphs, however, are indented.

% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.

% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.

% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}

% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}

% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
% %
% % ---- Bibliography ----
% %
% % BibTeX users should specify bibliography style 'splncs04'.
% % References will then be sorted and formatted in the correct style.
% %
% % \bibliographystyle{splncs04}
% % \bibliography{mybibliography}
% %
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\end{document}

### 2020-04-26 src/main/scala/w2d/Wireframe2DOM.scala
Merge changes

@@ -46,4 +46,5 @@ object Wireframe2DOM extends App {
     println(sectionizeRow(rects))
     null
   }
+
 }

### 2020-04-26 src/main/scala/w2d/DOMVisualizer.scala
Cross

@@ -5,7 +5,7 @@ import scalafx.application.JFXApp.PrimaryStage
 import scalafx.geometry.Insets
 import scalafx.scene.Scene
 import scalafx.scene.layout.Pane
-import scalafx.scene.shape.Rectangle
+import scalafx.scene.shape.{Line, Rectangle}
 
 class DOMVisualizer(rootContainer: Container, stageWidth: Int, stageHeight: Int) extends JFXApp {
   stage = new PrimaryStage {
@@ -13,7 +13,11 @@ class DOMVisualizer(rootContainer: Container, stageWidth: Int, stageHeight: Int)
     scene = new Scene {
       root = new Pane {
         padding = Insets(0)
-        children = DOMVisualizer.toRectangles(rootContainer) :+ {
+        children = DOMVisualizer.toRectangles(rootContainer, withBorderOnly = true).flatMap { rectangle =>
+          val diagonal1 = Line(rectangle.x.value, rectangle.y.value, rectangle.x.value + rectangle.width.value, rectangle.y.value + rectangle.height.value)
+          val diagonal2 = Line(rectangle.x.value + rectangle.width.value, rectangle.y.value, rectangle.x.value, rectangle.y.value + rectangle.height.value)
+          Seq(rectangle, diagonal1, diagonal2)
+        } :+ {
           val root = Rectangle(0, 0, stageWidth, stageHeight)
           root.style = "-fx-fill: transparent; -fx-stroke: red; -fx-stroke-width: 1;"
           root

### 2020-04-26 src/main/scala/w2d/Examples.scala

@@ -3,50 +3,37 @@ package w2d
 import scalafx.scene.paint.Color
 
 object Examples {
-  def Basic(): Unit = {
-    Wireframe2DOM.synthesize(
-      Seq(
-        Rect(Vector2(20, 20), Vector2(760, 120)),
-        Rect(Vector2(20, 160), Vector2(184, 184)),
-        Rect(Vector2(20 + 184 + 8, 160), Vector2(184, 184)),
-        Rect(Vector2(20 + 184 + 8 + 184 + 8, 160), Vector2(184, 184)),
-        Rect(Vector2(20 + 184 + 8 + 184 + 8 + 184 + 8, 160), Vector2(184, 184)),
-        Rect(Vector2(20, 370), Vector2(760, 200)),
-      ),
-      800,
-      600
-    )
-  }
+  def ComplexLayout(): Seq[Rect] = Seq(
+    Rect(Vector2(20, 10), Vector2(160, 30)),
+    Rect(Vector2(220, 10), Vector2(260, 30)),
+    Rect(Vector2(520, 10), Vector2(260, 30)),
+    Rect(Vector2(0, 50), Vector2(800, 140)),
+    Rect(Vector2(200, 220), Vector2(400, 20)),
+    Rect(Vector2(105, 265), Vector2(140, 145)),
+    Rect(Vector2(105, 415), Vector2(140, 20)),
+    Rect(Vector2(255, 265), Vector2(140, 145)),
+    Rect(Vector2(255, 415), Vector2(140, 20)),
+    Rect(Vector2(405, 265), Vector2(140, 145)),
+    Rect(Vector2(405, 415), Vector2(140, 20)),
+    Rect(Vector2(555, 265), Vector2(140, 145)),
+    Rect(Vector2(555, 415), Vector2(140, 20)),
+    Rect(Vector2(105, 445), Vector2(140, 145)),
+    Rect(Vector2(105, 595), Vector2(140, 20)),
+    Rect(Vector2(255, 445), Vector2(140, 145)),
+    Rect(Vector2(255, 595), Vector2(140, 20)),
+    Rect(Vector2(10, 650), Vector2(780, 30)),
+    Rect(Vector2(50, 700), Vector2(160, 160)),
+    Rect(Vector2(230, 700), Vector2(160, 160)),
+    Rect(Vector2(410, 700), Vector2(160, 160)),
+    Rect(Vector2(590, 700), Vector2(160, 160)),
[…]

### 2020-04-26 src/main/scala/w2d/Wireframe2DOM.scala

@@ -2,6 +2,7 @@ package w2d
 
 object Wireframe2DOM extends App {
   Examples.DOMVisualizerTest()
+  synthesize(Examples.ComplexLayout(), 800, 1200)
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
   def rectLowerX(rect: Rect): Int = {rect.origin.y + rect.size.y}
@@ -12,11 +13,11 @@ object Wireframe2DOM extends App {
   def sectionize(rects: Seq[Rect], rectLowerXY: Rect => Int, rectXY: Rect => Int): Seq[Seq[Rect]] = {
     val rectSortedByEnd = rects.sortWith(rectLowerXY(_) < rectLowerXY(_))
     // sort the rects' lower y and obtain all distinct values
-    val rectSorted = (rectSortedByEnd map {case rect => rectLowerXY(rect)}).toSet.toSeq.sortWith(_ < _)
-    val rectRange = rectSortedByEnd map {case rect => rectXY(rect) until rectLowerXY(rect)}
-    val clearRect = rectSorted filter {case row => (rectRange filter {case range => range.contains(row)}).length == 0}
+    val rectSorted = (rectSortedByEnd map (rect => rectLowerXY(rect))).distinct.sortWith(_ < _)
+    val rectRange = rectSortedByEnd map (rect => rectXY(rect) until rectLowerXY(rect))
+    val clearRect = rectSorted filter (row => (rectRange filter (range => range.contains(row))).length == 0)
     var addedUntil = 0
-    val cut : Map[Int, Seq[Rect]] = (clearRect map {case row =>
+    val cut : Map[Int, Seq[Rect]] = (clearRect map { row =>
       row -> {
         var rectSeq = Seq[Rect]()
         var counter = addedUntil
@@ -42,8 +43,10 @@ object Wireframe2DOM extends App {
 
   def synthesize(rects: Seq[Rect], width: Int, height: Int): Container = {
     //new WireframeVisualizer(rects, width, height).main(Array())
-    println(sectionizeCol(rects))
-    println(sectionizeRow(rects))
+    print("Sectionize col\n")
+    sectionizeCol(rects) foreach println
+    print("Sectionize row\n")
+    sectionizeRow(rects) foreach println
     null
   }
 

### 2020-04-27 src/main/scala/w2d/Wireframe2DOM.scala
TODO: grid and single line div

@@ -1,12 +1,14 @@
 package w2d
+import scalafx.scene.paint.Color
 
 object Wireframe2DOM extends App {
-  Examples.DOMVisualizerTest()
+  //Examples.DOMVisualizerTest()
+  val depthLimit:Int = 5;
+  val white = Color.White
   synthesize(Examples.ComplexLayout(), 800, 1200)
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
-  def rectLowerX(rect: Rect): Int = {rect.origin.y + rect.size.y}
-
+  def rectLowerX(rect: Rect): Int = {rect.origin.x + rect.size.x}
   def rectX(rect: Rect): Int = {rect.origin.x}
   def rectY(rect: Rect): Int = {rect.origin.y}
 
@@ -32,22 +34,67 @@ object Wireframe2DOM extends App {
 
     cut.toSeq.sortBy(_._1) map {case (_, section) => section}
   }
-
-  def sectionizeRow(rects : Seq[Rect]): Seq[Seq[Rect]] = {
-    sectionize(rects, rectLowerY, rectY)
+  def sectionizeRow(rects : Seq[Rect]): Seq[Seq[Rect]] = sectionize(rects, rectLowerY, rectY)
+  def sectionizeCol(rects : Seq[Rect]): Seq[Seq[Rect]] = sectionize(rects, rectLowerX, rectX)
+  
+  def sectionAnchor(sects : Seq[Seq[Rect]], sectsLower: Rect => Int, start: Int): Seq[Int] = {
+    if (sects.length == 0) {
+      Seq()
+    } else {
+      start +: (sects.init map {case sect => sect.map(rect => sectsLower(rect)).max})
+    } 
   }
+  def sectionAnchorRow(sects : Seq[Seq[Rect]], start: Int): Seq[Int] = sectionAnchor(sects, rectLowerY, start)
+  def sectionAnchorCol(sects : Seq[Seq[Rect]], start: Int): Seq[Int] = sectionAnchor(sects, rectLowerX, start)
 
-  def sectionizeCol(rects : Seq[Rect]): Seq[Seq[Rect]] = {
-    sectionize(rects, rectLowerX, rectX)
+  // recursively synthesis a section horizationly or vertically
+  // if row is true, the synthesis is conducted vertically
[…]

### 2020-04-27 src/main/scala/w2d/Models.scala
basic functionality synthesizer

@@ -5,6 +5,7 @@ import scalafx.scene.paint.{Color, Paint}
 case class Vector2(x: Int, y: Int) {
   def +(other: Vector2): Vector2 = Vector2(x + other.x, y + other.y)
   def -(other: Vector2): Vector2 = Vector2(x - other.x, y - other.y)
+  def ==(other: Vector2): Boolean = (x == other.x) && (y == other.y)
 }
 
 object Vector2 {
@@ -33,12 +34,17 @@ class Container {
 
   // For DOMVisualizer use only
   var origin: Vector2 = Vector2.Zero
+  def toString(depth: Int = 0): String = {
+    val thisStr = "\t" * depth + this.getClass().toString() + "(Size=(" +size.x + ","+size.y +") margin=("+margin.top + ","+margin.right + "," + margin.bottom  + "," +margin.left+"))\n"
+    (thisStr +:(children map {case child => child.toString(depth + 1)})).mkString("")
+  }
 }
 
 class HVContainer extends Container {
   var horizontal = true
   def isHorizontal: Boolean = horizontal
   def isVertical: Boolean = !isHorizontal
+  
 }
 
 class GridContainer extends Container {

### 2020-04-27 src/main/scala/w2d/Wireframe2DOM.scala

@@ -47,51 +47,262 @@ object Wireframe2DOM extends App {
   def sectionAnchorRow(sects : Seq[Seq[Rect]], start: Int): Seq[Int] = sectionAnchor(sects, rectLowerY, start)
   def sectionAnchorCol(sects : Seq[Seq[Rect]], start: Int): Seq[Int] = sectionAnchor(sects, rectLowerX, start)
 
+  def sectionLower(sects : Seq[Seq[Rect]], sectsLower: Rect => Int): Seq[Int] = {
+    if (sects.length == 0) {
+      Seq()
+    } else {
+      sects map {case sect => sect.map(rect => sectsLower(rect)).max}
+    } 
+  }
+  def sectionLowerRow(sects : Seq[Seq[Rect]]): Seq[Int] = sectionLower(sects, rectLowerY)
+  def sectionLowerCol(sects : Seq[Seq[Rect]]): Seq[Int] = sectionLower(sects, rectLowerX)
+
   // recursively synthesis a section horizationly or vertically
   // if row is true, the synthesis is conducted vertically
   def synthesizeHV(rects: Seq[Rect], width: Int, height: Int,x: Int = 0, y: Int = 0, depth: Int = 0, row: Boolean = true): Container = {
+    println(rects)
     if (rects.length == 0) {
       null
-    } else if (depth > depthLimit || rects.length == 1) {
+    } else if (depth > depthLimit) {
+      // bruteforce partition the graph into hdivs and vdivs
+      // dont search for grid
       null// plainDivs(rects, x, y)
+    } else if (rects.length == 1) {
+      val rect = rects.head
+      div(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x)
     }
     else {
       val sectionizeHV = if (row) sectionizeRow _ else sectionizeCol _
       val sectionizeHVReverse = if (!row) sectionizeRow _ else sectionizeCol _
       val sectionAnchorHV = if (row) sectionAnchorRow _ else sectionAnchorCol _
+      val sectionLowerHV = if (row) sectionLowerRow _ else sectionLowerCol _
       val anchorStart = if (row) y else x
       val hvdiv = if (row) vdiv _ else hdiv _
+      val hvdivReverse = if (row) hdiv _ else vdiv _
 
       val sections = sectionizeHV(rects)
       val sectionAnchors: Seq[Int] = sectionAnchorHV(sections, anchorStart)
-      // We know that singleHDiv are simple, linear horizontal divs
[…]

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
Html here we go

@@ -1,11 +1,15 @@
 package w2d
+import java.nio.charset.StandardCharsets
+import java.nio.file.{Files, Paths}
+
 import scalafx.scene.paint.Color
 
 object Wireframe2DOM extends App {
   //Examples.DOMVisualizerTest()
-  val depthLimit:Int = 5;
+  val depthLimit: Int = 5;
   val white = Color.White
-  synthesize(Examples.ComplexLayout(), 800, 1200)
+
+  new DOMVisualizer(synthesize(Examples.ComplexLayout(), 800, 1200), 800, 1200).main(Array())
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
   def rectLowerX(rect: Rect): Int = {rect.origin.x + rect.size.x}
@@ -294,17 +298,41 @@ object Wireframe2DOM extends App {
     
   }
 
-
   def synthesize(rects: Seq[Rect], width: Int, height: Int): Container = {
     val res = synthesizeHV(rects, width, height)
-    val convertedRectangles = DOMVisualizer.toRectangles(res, withBorderOnly = true)
-    print(s"Converted to ${convertedRectangles.length} rectangles:\n")
-    convertedRectangles.foreach { rectangle =>
-      print(s"Rect(Vector2(${rectangle.x.value.toInt}, ${rectangle.y.value.toInt}), Vector2(${rectangle.width.value.toInt}, ${rectangle.height.value.toInt})),\n")
-    }
+//    val convertedRectangles = DOMVisualizer.toRectangles(res, withBorderOnly = true)
+//    print(s"Converted to ${convertedRectangles.length} rectangles:\n")
+//    convertedRectangles.foreach { rectangle =>
+//      print(s"Rect(Vector2(${rectangle.x.value.toInt}, ${rectangle.y.value.toInt}), Vector2(${rectangle.width.value.toInt}, ${rectangle.height.value.toInt})),\n")
+//    }
+    println("=== Result ===")
+    println(res.toString(0))
+    val html = "<html>\n<body>\n" + toHtml(res)(1) + "\n</body>\n</html>"
+    println(html)
+    Files.write(Paths.get("result.html"), html.getBytes(StandardCharsets.UTF_8))
     res
   }
 
+  def toHtml(container: Container)(implicit tabs: Int = 0): String = {
+    var style = ""
+    style += s"width: ${container.size.x}px; "
+    style += s"height: ${container.size.y}px; "
[…]

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
minor fixed

@@ -5,6 +5,7 @@ object Wireframe2DOM extends App {
   //Examples.DOMVisualizerTest()
   val depthLimit:Int = 5;
   val white = Color.White
+  println(Examples.ComplexLayout())
   synthesize(Examples.ComplexLayout(), 800, 1200)
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
@@ -251,7 +252,8 @@ object Wireframe2DOM extends App {
       }}
       // TODO add the computed children to childrenlist
       childrenList = ((complexSections ++ gridList) sortWith {case ((index1, _), (index2, _)) => index1 < index2}) map {case (_, sect) => sect}
-      val res = hvdiv(width, height, white, false, 0, 0, 0, 0)(childrenList)
+
+      val res = if(childrenList.length == 1) childrenList.head else hvdiv(width, height, white, false, 0, 0, 0, 0)(childrenList)
       println(res.toString(0))
       res
       

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
grid changed

@@ -8,13 +8,8 @@ object Wireframe2DOM extends App {
   //Examples.DOMVisualizerTest()
   val depthLimit: Int = 5;
   val white = Color.White
-<<<<<<< HEAD
-  println(Examples.ComplexLayout())
-  synthesize(Examples.ComplexLayout(), 800, 1200)
-=======
 
   new DOMVisualizer(synthesize(Examples.ComplexLayout(), 800, 1200), 800, 1200).main(Array())
->>>>>>> 41b5078952f885ff464630424492c6d16f9efabc
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
   def rectLowerX(rect: Rect): Int = {rect.origin.x + rect.size.x}
@@ -131,12 +126,13 @@ object Wireframe2DOM extends App {
         val cellChildren = childrenHVContainer(rects, cellx, celly, !row)
         hvdiv(cellWidth, cellHeight, white, false, 0, 0, 0, 0)(cellChildren)
       }
-      def generateGrid(start: Int, end: Int, n: Int): Container = {
-        // TODO variable length element of cell need recursion
+      def generateGrid(start: Int, end: Int, n: Int, x: Int, y: Int): Container = {
+        // TODO variable length element of cell need recursion 
         val sectionX = if (row) x else sectionAnchors(start)
         val sectionY = if (row) sectionAnchors(start) else y
         val firstOrigin = possibleGridSectMap(start).head.origin
         val (gridX, gridY) = (firstOrigin.x, firstOrigin.y)
+        val (leftMargin, topMargin) = (gridX - x, gridY - y)
         val sectionWidth = if (row) width else sectionLowers(end) - sectionX
         val sectionHeight = if (row) sectionLowers(end) - sectionY else height
         var cellList = Seq[Container]()
@@ -180,7 +176,7 @@ object Wireframe2DOM extends App {
             processed = processed + n
           }
         }
-        grid(sectionWidth, sectionHeight, border = false)(cellList: _*)
+        grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin)(cellList: _*)
       }
 
       var unsuccessfulGrid = Seq[(Int, Seq[Rect])]()
@@ -236,7 +232,9 @@ object Wireframe2DOM extends App {
               val upToSize = sameSize(validSize)._1 + dist - 1
               // now try to form a grid
               (index to upToSize) foreach {case i => addedToGrid(i) = true}
[…]

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
height fixed

@@ -156,9 +156,9 @@ object Wireframe2DOM extends App {
             } else {
               possibleGridSectMap(start)(1).origin.x - possibleGridSectMap(start)(0).origin.x
             }
-            cellHeight = possibleGridSectMap(start)(n).origin.y - possibleGridSectMap(start)(0).origin.y
+            cellHeight = possibleGridSectMap(start+n)(0).origin.y - possibleGridSectMap(start)(0).origin.y
           } else {
-            cellWidth = possibleGridSectMap(start)(n).origin.x - possibleGridSectMap(start)(0).origin.x
+            cellWidth = possibleGridSectMap(start+n)(0).origin.x - possibleGridSectMap(start)(0).origin.x
             cellHeight = if (possibleGridSectMap(start).length == 1) {
               possibleGridSectMap(start).head.size.y
             } else {
@@ -176,7 +176,7 @@ object Wireframe2DOM extends App {
             processed = processed + n
           }
         }
-        grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin)(cellList: _*)
+        grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin )(cellList: _*)
       }
 
       var unsuccessfulGrid = Seq[(Int, Seq[Rect])]()

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
grid width and height fixed

@@ -131,10 +131,11 @@ object Wireframe2DOM extends App {
         val sectionX = if (row) x else sectionAnchors(start)
         val sectionY = if (row) sectionAnchors(start) else y
         val firstOrigin = possibleGridSectMap(start).head.origin
+        val lastRect = possibleGridSectMap(start).last
         val (gridX, gridY) = (firstOrigin.x, firstOrigin.y)
         val (leftMargin, topMargin) = (gridX - x, gridY - y)
-        val sectionWidth = if (row) width else sectionLowers(end) - sectionX
-        val sectionHeight = if (row) sectionLowers(end) - sectionY else height
+        val sectionWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX  else sectionLowers(end) - sectionX
+        val sectionHeight = if (row) sectionLowers(end) - sectionY else lastRect.origin.y + lastRect.size.y - gridY
         var cellList = Seq[Container]()
         var processed = start
         var (gridWidth, gridHeight) = (0, 0)

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
grid width and height

@@ -134,8 +134,8 @@ object Wireframe2DOM extends App {
         val lastRect = possibleGridSectMap(start).last
         val (gridX, gridY) = (firstOrigin.x, firstOrigin.y)
         val (leftMargin, topMargin) = (gridX - x, gridY - y)
-        val sectionWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX  else sectionLowers(end) - sectionX
-        val sectionHeight = if (row) sectionLowers(end) - sectionY else lastRect.origin.y + lastRect.size.y - gridY
+        var sectionWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX  else sectionLowers(end) - sectionX
+        var sectionHeight = if (row) sectionLowers(end) - sectionY else lastRect.origin.y + lastRect.size.y - gridY
         var cellList = Seq[Container]()
         var processed = start
         var (gridWidth, gridHeight) = (0, 0)
@@ -176,6 +176,14 @@ object Wireframe2DOM extends App {
             }
             processed = processed + n
           }
+        }
+        if (row) {
+          sectionWidth = cellWidth * possibleGridSectMap(start).length
+          sectionHeight = (possibleGridSectMap(start+n)(0).origin.y - possibleGridSectMap(start)(0).origin.y) * (end + 1 - start) / n
+        }
+        else {
+          sectionWidth = (possibleGridSectMap(start+n)(0).origin.x - possibleGridSectMap(start)(0).origin.x) * (end + 1 - start) / n
+          sectionHeight = cellHeight * possibleGridSectMap(start).length
         }
         grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin )(cellList: _*)
       }

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
added missing div

@@ -64,7 +64,7 @@ object Wireframe2DOM extends App {
   // recursively synthesis a section horizationly or vertically
   // if row is true, the synthesis is conducted vertically
   def synthesizeHV(rects: Seq[Rect], width: Int, height: Int,x: Int = 0, y: Int = 0, depth: Int = 0, row: Boolean = true): Container = {
-    println(rects)
+    //println(rects)
     if (rects.length == 0) {
       null
     } else if (depth > depthLimit) {
@@ -245,11 +245,10 @@ object Wireframe2DOM extends App {
               val gridY = if (row) sectionAnchors(index) else y
               gridList = gridList :+ ((index, generateGrid(index, upToSize, dist, gridX, gridY)))
               // TODO add fail case
-              i = upToSize + 1
+              i = i + upToSize - index + 1
             } 
           }
         }
-
         // TODO increase i
         if (!success) {
           addedToGrid(i) = true
@@ -257,7 +256,6 @@ object Wireframe2DOM extends App {
           i = i + 1
         }
       }
-      
       val complexSections = (unsuccessfulGrid ++ complexStructure ++ complexStrip) map {case (index, section) => {
         val sectionX = if (row) x else sectionAnchors(index)
         val sectionY = if (row) sectionAnchors(index) else y
@@ -269,7 +267,6 @@ object Wireframe2DOM extends App {
       childrenList = ((complexSections ++ gridList) sortWith {case ((index1, _), (index2, _)) => index1 < index2}) map {case (_, sect) => sect}
 
       val res = if(childrenList.length == 1) childrenList.head else hvdiv(width, height, white, false, 0, 0, 0, 0)(childrenList)
-      println(res.toString(0))
       res
       
     }

### 2020-04-30 src/main/scala/w2d/Models.scala
minwidth added

@@ -48,4 +48,5 @@ class HVContainer extends Container {
 }
 
 class GridContainer extends Container {
+  var minWidth: Int = 0
 }

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala

@@ -177,6 +177,7 @@ object Wireframe2DOM extends App {
             processed = processed + n
           }
         }
+        val minWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX else sectionLowers(end) - sectionX
         if (row) {
           sectionWidth = cellWidth * possibleGridSectMap(start).length
           sectionHeight = (possibleGridSectMap(start+n)(0).origin.y - possibleGridSectMap(start)(0).origin.y) * (end + 1 - start) / n
@@ -185,7 +186,7 @@ object Wireframe2DOM extends App {
           sectionWidth = (possibleGridSectMap(start+n)(0).origin.x - possibleGridSectMap(start)(0).origin.x) * (end + 1 - start) / n
           sectionHeight = cellHeight * possibleGridSectMap(start).length
         }
-        grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin )(cellList: _*)
+        grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin, minWidth = minWidth)(cellList: _*)
       }
 
       var unsuccessfulGrid = Seq[(Int, Seq[Rect])]()

### 2020-04-30 src/main/scala/w2d/package.scala

@@ -25,10 +25,11 @@ package object w2d {
     container
   }
 
-  def grid(width: Int, height: Int, fill: Color = Color.White, border: Boolean = true, top: Int = 0, right: Int = 0, bottom: Int = 0, left: Int = 0)(children: Container*): GridContainer = {
+  def grid(width: Int, height: Int, fill: Color = Color.White, border: Boolean = true, top: Int = 0, right: Int = 0, bottom: Int = 0, left: Int = 0, minWidth: Int = 0)(children: Container*): GridContainer = {
     val container = new GridContainer
     container.fill = fill
     container.border = border
+    container.minWidth = minWidth
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
     children foreach { it => it.parent = container }

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
minwidth fixed

@@ -177,7 +177,7 @@ object Wireframe2DOM extends App {
             processed = processed + n
           }
         }
-        val minWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX else sectionLowers(end) - sectionX
+        val minWidth = if (row) lastRect.origin.x + lastRect.size.x - gridX else sectionLowers(end) - gridX
         if (row) {
           sectionWidth = cellWidth * possibleGridSectMap(start).length
           sectionHeight = (possibleGridSectMap(start+n)(0).origin.y - possibleGridSectMap(start)(0).origin.y) * (end + 1 - start) / n
@@ -186,6 +186,7 @@ object Wireframe2DOM extends App {
           sectionWidth = (possibleGridSectMap(start+n)(0).origin.x - possibleGridSectMap(start)(0).origin.x) * (end + 1 - start) / n
           sectionHeight = cellHeight * possibleGridSectMap(start).length
         }
+        println(minWidth)
         grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin, minWidth = minWidth)(cellList: _*)
       }
 

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
taowa

@@ -73,7 +73,8 @@ object Wireframe2DOM extends App {
       null// plainDivs(rects, x, y)
     } else if (rects.length == 1) {
       val rect = rects.head
-      div(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x)
+      val childrenDiv = div(rect.size.x, rect.size.y)
+      vdiv(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x)(childrenDiv)
     }
     else {
       val sectionizeHV = if (row) sectionizeRow _ else sectionizeCol _
@@ -186,7 +187,6 @@ object Wireframe2DOM extends App {
           sectionWidth = (possibleGridSectMap(start+n)(0).origin.x - possibleGridSectMap(start)(0).origin.x) * (end + 1 - start) / n
           sectionHeight = cellHeight * possibleGridSectMap(start).length
         }
-        println(minWidth)
         grid(sectionWidth, sectionHeight, border = false, top = topMargin, left = leftMargin, minWidth = minWidth)(cellList: _*)
       }
 

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala
border fiexed

@@ -74,7 +74,7 @@ object Wireframe2DOM extends App {
     } else if (rects.length == 1) {
       val rect = rects.head
       val childrenDiv = div(rect.size.x, rect.size.y)
-      vdiv(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x)(childrenDiv)
+      vdiv(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x, border = false)(childrenDiv)
     }
     else {
       val sectionizeHV = if (row) sectionizeRow _ else sectionizeCol _

### 2020-04-30 src/main/scala/w2d/DOMVisualizer.scala
Responsive!!

@@ -13,13 +13,15 @@ class DOMVisualizer(rootContainer: Container, stageWidth: Int, stageHeight: Int)
     scene = new Scene {
       root = new Pane {
         padding = Insets(0)
-        children = DOMVisualizer.toRectangles(rootContainer, withBorderOnly = true).flatMap { rectangle =>
-          val diagonal1 = Line(rectangle.x.value, rectangle.y.value, rectangle.x.value + rectangle.width.value, rectangle.y.value + rectangle.height.value)
-          val diagonal2 = Line(rectangle.x.value + rectangle.width.value, rectangle.y.value, rectangle.x.value, rectangle.y.value + rectangle.height.value)
-          Seq(rectangle, diagonal1, diagonal2)
+        children = DOMVisualizer.toRectangles(rootContainer).flatMap { rectangle =>
+          if (rectangle.userData == "div") {
+            val diagonal1 = Line(rectangle.x.value, rectangle.y.value, rectangle.x.value + rectangle.width.value, rectangle.y.value + rectangle.height.value)
+            val diagonal2 = Line(rectangle.x.value + rectangle.width.value, rectangle.y.value, rectangle.x.value, rectangle.y.value + rectangle.height.value)
+            Seq(rectangle, diagonal1, diagonal2)
+          } else Seq(rectangle)
         } :+ {
           val root = Rectangle(0, 0, stageWidth, stageHeight)
-          root.style = "-fx-fill: transparent; -fx-stroke: red; -fx-stroke-width: 1;"
+          root.style = "-fx-fill: transparent; -fx-stroke: black; -fx-stroke-width: 1;"
           root
         }
     }
@@ -30,15 +32,33 @@ class DOMVisualizer(rootContainer: Container, stageWidth: Int, stageHeight: Int)
 }
 
 object DOMVisualizer {
-  def toRectangles(container: Container, withBorderOnly: Boolean = false): Seq[Rectangle] = {
+  def toRectangles(container: Container, withBorderOnly: Boolean = false, depth: Int = 0): Seq[Rectangle] = {
     calculateAbsoluteOrigin(container)
 
-    val rectangle = Rectangle(container.origin.x, container.origin.y, container.size.x, container.size.y)
-    if (container.border) rectangle.style = "-fx-stroke: black; -fx-stroke-width: 1;"
-    else rectangle.style = "-fx-stroke-width: 0;"
+    var trueWidth = container.size.x
+    container match {
+      case gridContainer: GridContainer =>
[…]

### 2020-04-30 src/main/scala/w2d/Wireframe2DOM.scala

@@ -8,8 +8,13 @@ object Wireframe2DOM extends App {
   //Examples.DOMVisualizerTest()
   val depthLimit: Int = 5;
   val white = Color.White
+  var synthesized = synthesize(Examples.ComplexLayout(), 800, 1200)
 
-  new DOMVisualizer(synthesize(Examples.ComplexLayout(), 800, 1200), 800, 1200).main(Array())
+  new DOMVisualizer(synthesized, 800, 1200)//.main(Array())
+
+  val html = toHtml(synthesized, 800, 1200)
+  println(html)
+  Files.write(Paths.get("result.html"), html.getBytes(StandardCharsets.UTF_8))
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
   def rectLowerX(rect: Rect): Int = {rect.origin.x + rect.size.x}
@@ -74,7 +79,7 @@ object Wireframe2DOM extends App {
     } else if (rects.length == 1) {
       val rect = rects.head
       val childrenDiv = div(rect.size.x, rect.size.y)
-      vdiv(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x, border = false)(childrenDiv)
+      hdiv(rect.size.x, rect.size.y, top = rect.origin.y - y, left = rect.origin.x - x, border = false)(childrenDiv)
     }
     else {
       val sectionizeHV = if (row) sectionizeRow _ else sectionizeCol _
@@ -319,33 +324,73 @@ object Wireframe2DOM extends App {
 //    }
     println("=== Result ===")
     println(res.toString(0))
-    val html = "<html>\n<body>\n" + toHtml(res)(1) + "\n</body>\n</html>"
-    println(html)
-    Files.write(Paths.get("result.html"), html.getBytes(StandardCharsets.UTF_8))
     res
   }
 
-  def toHtml(container: Container)(implicit tabs: Int = 0): String = {
-    var style = ""
-    style += s"width: ${container.size.x}px; "
-    style += s"height: ${container.size.y}px; "
-    style += s"margin: ${container.margin.top}px ${container.margin.right}px ${container.margin.bottom}px ${container.margin.left}px; "
-    if (container.border) style += s"border: 2px solid black; "
-    container.parent match {
-      case hvContainer: HVContainer =>
-        if (hvContainer.isHorizontal) {
-          style += "display: inline-block; "
-        }
-      case gridContainer: GridContainer =>
+  def toHtml(container: Container, stageWidth: Int, stageHeight: Int): String = {
[…]

### 2020-05-01 src/main/scala/w2d/Examples.scala
wtf

@@ -1,104 +1,99 @@
 package w2d
 
-import scalafx.scene.paint.Color
-
 object Examples {
-  def ComplexLayout(): Seq[Rect] = Seq(
-    Rect(Vector2(20, 10), Vector2(160, 30)),
-    Rect(Vector2(220, 10), Vector2(260, 30)),
-    Rect(Vector2(520, 10), Vector2(260, 30)),
-    Rect(Vector2(0, 50), Vector2(800, 140)),
-    Rect(Vector2(200, 220), Vector2(400, 20)),
-    Rect(Vector2(105, 265), Vector2(140, 145)),
-    Rect(Vector2(105, 415), Vector2(140, 20)),
-    Rect(Vector2(255, 265), Vector2(140, 145)),
-    Rect(Vector2(255, 415), Vector2(140, 20)),
-    Rect(Vector2(405, 265), Vector2(140, 145)),
-    Rect(Vector2(405, 415), Vector2(140, 20)),
-    Rect(Vector2(555, 265), Vector2(140, 145)),
-    Rect(Vector2(555, 415), Vector2(140, 20)),
-    Rect(Vector2(105, 445), Vector2(140, 145)),
-    Rect(Vector2(105, 595), Vector2(140, 20)),
-    Rect(Vector2(255, 445), Vector2(140, 145)),
-    Rect(Vector2(255, 595), Vector2(140, 20)),
-    Rect(Vector2(10, 650), Vector2(780, 30)),
-    Rect(Vector2(50, 700), Vector2(160, 160)),
-    Rect(Vector2(230, 700), Vector2(160, 160)),
-    Rect(Vector2(410, 700), Vector2(160, 160)),
-    Rect(Vector2(590, 700), Vector2(160, 160)),
-    Rect(Vector2(30, 880), Vector2(440, 100)),
-    Rect(Vector2(490, 890), Vector2(80, 80)),
-    Rect(Vector2(590, 890), Vector2(80, 80)),
-    Rect(Vector2(690, 890), Vector2(80, 80)),
-  )
 
-  def WireframeVisualizerTest(): Unit = {
-    new WireframeVisualizer(ComplexLayout(), 800, 1000).main(Array())
+  def toRect(container: Container): Seq[Rect] = {
+    DOMVisualizer.toRectangles(container, withBorderOnly = true).map { rectangle =>
[…]

### 2020-05-01 document/paper.tex

@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-15--250 words.
+We propose a lightweight program synthesizer that generates HTML from static Wireframe design graph.
+With our program, a UI/UX designer with little or no programming experience can obtain responsive HTML from design layout.
 
@@
 \section{Introduction}
+Program synthesis community targets mainly on string processing and integer manipulating problem.
+However, the need for generating web application and other Graphical User Interface(GUI) applications is growing.
+While some UI/UX designers are capable of writing frontend code, providing them with a tool that generating HTML code can be beneficial.
+With HTML code equivalent to their interface design, designers can edit, test, and improve the original static layout.
+For example, many web applications now seek compatibility between PC and mobile devices.
+The different sizes complicate the designers' work.
+Some layouts are more promising on $16:9$ screen than on other smart devices.
+With the responsive HTML generated by our project, designer can preview the layout in a new resolution without re-drawing.
+
+Our work focuses on configure the relationship between each atom elements in the static layout.
+We combine components of different sizes and locations into horizontal/vertical divisions and grids.
+Instead of the absolute coordinate given by input, we assign margin to the converted structure and remember the relative position between them.
+Without the limitation of absolute coordinates, the converted structures can be rendered with the designers' true intention.
+
+\section{Related work}
+% Tiger
+
+\section{Illustrative example}
+% Shangyin
 \section{Background}
-\section{Related work}
-\section{Illustrative example}
+% Shangyin
 \section{Formal problem definition}
+% Shangyin
 \section{Algorithm}
+% Shangyin
+\subsection{Workflow}
+Static Graph (the absolute location of each component) $=>$ relative intermediate representation $=>$HTML
+\subsection{Grammar}
+\subsubsection{Input}
+RECT\\
+RECTLIST:= RECTLIST RECT | Nil
+\subsubsection{IR}
+DIV\\
+HDIV:= HDIV|DIV|VDIV\\
+VDIV:= HDIV|DIV|VDIV\\
 First we divide the rectangles into section based on their $y$-axis. Then we use
-greedy to find the earlist possible cut $y$ such that this $y$ does not divide any
+greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
 other rects.
+
 \section{Evaluation}
+% Tiger
 \section{Conclusion}
+% Tiger
 
-%\subsection{A Subsection Sample}
-
-% Please note that the first paragraph of a section or subsection is
-% not indented. The first paragraph that follows a table, figure,
-% equation etc. does not need an indent, either.
-
-% Subsequent paragraphs, however, are indented.
-
-% \subsubsection{Sample Heading (Third Level)} Only two levels of
-% headings should be numbered. Lower level headings remain unnumbered;
-% they are formatted as run-in headings.
-
-% \paragraph{Sample Heading (Fourth Level)}
-% The contribution should contain no more than four levels of
-% headings. Table~\ref{tab1} gives a summary of all heading levels.
-
-% \begin{table}
-% \caption{Table captions should be placed above the
-% tables.}\label{tab1}
-% \begin{tabular}{|l|l|l|}
-% \hline
-% Heading level &  Example & Font size and style\\
-% \hline
-% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
-% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
-% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
-% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
-% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \noindent Displayed equations are centered and set on a separate
-% line.
-% \begin{equation}
-% x + y = z
-% \end{equation}
-% Please try to avoid rasterized images for line-art diagrams and
-% schemas. Whenever possible, use vector graphics instead (see
-% Fig.~\ref{fig1}).
-
-% \begin{figure}
-% \includegraphics[width=\textwidth]{fig1.eps}
-% \caption{A figure caption is always placed below the illustration.
-% Please note that short captions are centered, while long ones are
-% justified by the macro package automatically.} \label{fig1}
-% \end{figure}
-
-% \begin{theorem}
-% This is a sample theorem. The run-in heading is set in bold, while
-% the following text appears in italics. Definitions, lemmas,
-% propositions, and corollaries are styled the same way.
-% \end{theorem}
-% %
-% % the environments 'definition', 'lemma', 'proposition', 'corollary',
-% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
-% %
-% \begin{proof}
-% Proofs, examples, and remarks have the initial word in italics,
-% while the following text appears in normal font.
-% \end{proof}
-% For citations of references, we prefer the use of square brackets
-% and consecutive numbers. Citations using labels or the author/year
-% convention are also acceptable. The following bibliography provides
-% a sample reference list with entries for journal
-% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
-% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
-% and a homepage~\cite{ref_url1}. Multiple citations are grouped
-% \cite{ref_article1,ref_lncs1,ref_book1},
-% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
-% %
-% % ---- Bibliography ----
-% %
-% % BibTeX users should specify bibliography style 'splncs04'.
-% % References will then be sorted and formatted in the correct style.
-% %
-% % \bibliographystyle{splncs04}
-% % \bibliography{mybibliography}
-% %
-% \begin{thebibliography}{8}
-% \bibitem{ref_article1}
-% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
-
-% \bibitem{ref_lncs1}
-% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-% \bibitem{ref_book1}
-% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
-% Location (1999)
-
-% \bibitem{ref_proc1}
-% Author, A.-B.: Contribution title. In: 9th International Proceedings
-% on Proceedings, pp. 1--2. Publisher, Location (2010)
-
-% \bibitem{ref_url1}
-% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
-% Oct 2017
-% \end{thebibliography}
 \end{document}

### 2020-05-01 src/main/scala/w2d/DOMVisualizer.scala
Revert "wtf"
This reverts commit 7d104f01

@@ -4,33 +4,27 @@ import scalafx.application.JFXApp
 import scalafx.application.JFXApp.PrimaryStage
 import scalafx.geometry.Insets
 import scalafx.scene.Scene
-import scalafx.scene.layout.{BorderPane, HBox, Pane, StackPane}
+import scalafx.scene.layout.Pane
 import scalafx.scene.shape.{Line, Rectangle}
 
 class DOMVisualizer(rootContainer: Container, stageWidth: Int, stageHeight: Int) extends JFXApp {
   stage = new PrimaryStage {
     title = "DOM Visualizer"
     scene = new Scene {
-      root = {
-        val pane = new Pane() {
-          children = DOMVisualizer.toRectangles(rootContainer).flatMap { rectangle =>
-            if (rectangle.userData == "div") {
-              val diagonal1 = Line(rectangle.x.value, rectangle.y.value, rectangle.x.value + rectangle.width.value, rectangle.y.value + rectangle.height.value)
-              val diagonal2 = Line(rectangle.x.value + rectangle.width.value, rectangle.y.value, rectangle.x.value, rectangle.y.value + rectangle.height.value)
-              Seq(rectangle, diagonal1, diagonal2)
-            } else Seq(rectangle)
-          } :+ {
-            val root = Rectangle(0, 0, stageWidth, stageHeight)
-            root.style = "-fx-fill: transparent; -fx-stroke: black; -fx-stroke-width: 1;"
-            root
-          }
+      root = new Pane {
+        padding = Insets(0)
+        children = DOMVisualizer.toRectangles(rootContainer).flatMap { rectangle =>
+          if (rectangle.userData == "div") {
+            val diagonal1 = Line(rectangle.x.value, rectangle.y.value, rectangle.x.value + rectangle.width.value, rectangle.y.value + rectangle.height.value)
+            val diagonal2 = Line(rectangle.x.value + rectangle.width.value, rectangle.y.value, rectangle.x.value, rectangle.y.value + rectangle.height.value)
+            Seq(rectangle, diagonal1, diagonal2)
+          } else Seq(rectangle)
+        } :+ {
+          val root = Rectangle(0, 0, stageWidth, stageHeight)
+          root.style = "-fx-fill: transparent; -fx-stroke: black; -fx-stroke-width: 1;"
+          root
         }
-        val root = new HBox {
-          padding = Insets(25, 25, 25, 25)
-          children = List(pane)
-        }
-        root
[…]

### 2020-05-01 src/main/scala/w2d/Examples.scala

@@ -1,99 +1,104 @@
 package w2d
 
+import scalafx.scene.paint.Color
+
 object Examples {
-
-  def toRect(container: Container): Seq[Rect] = {
-    DOMVisualizer.toRectangles(container, withBorderOnly = true).map { rectangle =>
-      Rect(Vector2(rectangle.x.value.toInt, rectangle.y.value.toInt), Vector2(rectangle.width.value.toInt, rectangle.height.value.toInt))
-    }
-  }
-
-  val examples = List(
-    // Example 1
-    vdiv(800, 600, border = false)(
-      div(800, 200),
-      div(760, 190, top = 10, left = 20, right = 20),
-      div(720, 190, top = 10, left = 40, right = 40)
-    ),
-    // Example 2
-    hdiv(800, 600, border = false)(
-      div(420, 580, top = 10, bottom = 10, left = 20),
-      div(200, 580, top = 10, bottom = 10, left = 20),
-      div(100, 580, top = 10, bottom = 10, left = 20, right = 20)
-    ),
-    // Example 3
-    vdiv(800, 1000, border = false)(
-      component1()
-    ),
-    // Example 4
-    vdiv(800, 10000, border = false)(
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-    )
+  def ComplexLayout(): Seq[Rect] = Seq(
+    Rect(Vector2(20, 10), Vector2(160, 30)),
+    Rect(Vector2(220, 10), Vector2(260, 30)),
+    Rect(Vector2(520, 10), Vector2(260, 30)),
+    Rect(Vector2(0, 50), Vector2(800, 140)),
+    Rect(Vector2(200, 220), Vector2(400, 20)),
+    Rect(Vector2(105, 265), Vector2(140, 145)),
+    Rect(Vector2(105, 415), Vector2(140, 20)),
+    Rect(Vector2(255, 265), Vector2(140, 145)),
+    Rect(Vector2(255, 415), Vector2(140, 20)),
+    Rect(Vector2(405, 265), Vector2(140, 145)),
+    Rect(Vector2(405, 415), Vector2(140, 20)),
+    Rect(Vector2(555, 265), Vector2(140, 145)),
+    Rect(Vector2(555, 415), Vector2(140, 20)),
[…]

### 2020-05-01 src/main/scala/w2d/Wireframe2DOM.scala

@@ -5,32 +5,16 @@ import java.nio.file.{Files, Paths}
 import scalafx.scene.paint.Color
 
 object Wireframe2DOM extends App {
-  for (c <- 1 to 100) {
-    println("==========")
-    for ((container, i) <- Examples.examples.view.zipWithIndex) {
-      val rectangles = Examples.toRect(container)
-      println(s"Converted to ${rectangles.length} rectangles:")
-      println(rectangles)
-      val (width, height) = (container.size.x, container.size.y)
-      val synthesized: Container = time(s"Synthesize example $i") {
-        synthesize(rectangles, width, height)
-      }
-      if (synthesized == null) println("草")
-      val html = time(s"Convert example $i to DOM") {
-        toHtml(synthesized, width)
-      }
-      Files.write(Paths.get(s"example$i.html"), html.getBytes(StandardCharsets.UTF_8))
-    }
-  }
-
+  //Examples.DOMVisualizerTest()
   val depthLimit: Int = 5;
   val white = Color.White
+  var synthesized = synthesize(Examples.ComplexLayout(), 800, 1200)
 
-  /*var synthesized = synthesize(Examples.ComplexLayout(), 800, 1200)
   new DOMVisualizer(synthesized, 800, 1200)//.main(Array())
+
   val html = toHtml(synthesized, 800, 1200)
   println(html)
-  Files.write(Paths.get("result.html"), html.getBytes(StandardCharsets.UTF_8))*/
+  Files.write(Paths.get("result.html"), html.getBytes(StandardCharsets.UTF_8))
 
   def rectLowerY(rect: Rect): Int = {rect.origin.y + rect.size.y}
   def rectLowerX(rect: Rect): Int = {rect.origin.x + rect.size.x}
@@ -332,17 +316,23 @@ object Wireframe2DOM extends App {
   }
 
   def synthesize(rects: Seq[Rect], width: Int, height: Int): Container = {
-    val container = synthesizeHV(rects, width, height)
-    print(container.toString(0))
-    container
+    val res = synthesizeHV(rects, width, height)
+//    val convertedRectangles = DOMVisualizer.toRectangles(res, withBorderOnly = true)
+//    print(s"Converted to ${convertedRectangles.length} rectangles:\n")
+//    convertedRectangles.foreach { rectangle =>
[…]

### 2020-05-01 src/main/scala/w2d/WireframeVisualizer.scala

@@ -12,6 +12,7 @@ class WireframeVisualizer(rects: Seq[Rect], stageWidth: Int, stageHeight: Int) e
     title = "Wireframe Visualizer"
     scene = new Scene {
       root = new Pane {
+        padding = Insets(0)
         children = {
           val root = Rectangle(0, 0, stageWidth, stageHeight)
           root.style = "-fx-fill: white; -fx-stroke: red; -fx-stroke-width: 1;"

### 2020-05-01 src/main/scala/w2d/package.scala

@@ -8,9 +8,8 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
-    nonNullChildren foreach { it => it.parent = container }
-    container.children = nonNullChildren
+    children foreach { it => it.parent = container }
+    container.children = children
     container
   }
 
@@ -21,9 +20,8 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
-    nonNullChildren foreach { it => it.parent = container }
-    container.children = nonNullChildren
+    children foreach { it => it.parent = container }
+    container.children = children
     container
   }
 
@@ -34,9 +32,8 @@ package object w2d {
     container.minWidth = minWidth
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
-    nonNullChildren foreach { it => it.parent = container }
-    container.children = nonNullChildren
+    children foreach { it => it.parent = container }
+    container.children = children
     container
   }
 

### 2020-05-01 src/main/scala/w2d/WireframeVisualizer.scala
Revert "Revert "wtf""
This reverts commit 3802d5d0

@@ -12,7 +12,6 @@ class WireframeVisualizer(rects: Seq[Rect], stageWidth: Int, stageHeight: Int) e
     title = "Wireframe Visualizer"
     scene = new Scene {
       root = new Pane {
-        padding = Insets(0)
         children = {
           val root = Rectangle(0, 0, stageWidth, stageHeight)
           root.style = "-fx-fill: white; -fx-stroke: red; -fx-stroke-width: 1;"

### 2020-05-01 src/main/scala/w2d/package.scala

@@ -8,8 +8,9 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    children foreach { it => it.parent = container }
-    container.children = children
+    val nonNullChildren = children.filter(it => it != null)
+    nonNullChildren foreach { it => it.parent = container }
+    container.children = nonNullChildren
     container
   }
 
@@ -20,8 +21,9 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    children foreach { it => it.parent = container }
-    container.children = children
+    val nonNullChildren = children.filter(it => it != null)
+    nonNullChildren foreach { it => it.parent = container }
+    container.children = nonNullChildren
     container
   }
 
@@ -32,8 +34,9 @@ package object w2d {
     container.minWidth = minWidth
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    children foreach { it => it.parent = container }
-    container.children = children
+    val nonNullChildren = children.filter(it => it != null)
+    nonNullChildren foreach { it => it.parent = container }
+    container.children = nonNullChildren
     container
   }
 

### 2020-05-01 src/main/scala/w2d/Wireframe2DOM.scala
fixxi

@@ -4,9 +4,15 @@ import java.nio.file.{Files, Paths}
 
 import scalafx.scene.paint.Color
 
+import scala.collection.immutable.ArraySeq
+
 object Wireframe2DOM extends App {
+  val depthLimit: Int = 5;
+  val white = Color.White
+
   for (c <- 1 to 100) {
     println("==========")
+
     for ((container, i) <- Examples.examples.view.zipWithIndex) {
       val rectangles = Examples.toRect(container)
       println(s"Converted to ${rectangles.length} rectangles:")
@@ -22,9 +28,6 @@ object Wireframe2DOM extends App {
       Files.write(Paths.get(s"example$i.html"), html.getBytes(StandardCharsets.UTF_8))
     }
   }
-
-  val depthLimit: Int = 5;
-  val white = Color.White
 
   /*var synthesized = synthesize(Examples.ComplexLayout(), 800, 1200)
   new DOMVisualizer(synthesized, 800, 1200)//.main(Array())

### 2020-05-01 src/main/scala/w2d/package.scala

@@ -8,7 +8,7 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
+    val nonNullChildren = children
     nonNullChildren foreach { it => it.parent = container }
     container.children = nonNullChildren
     container
@@ -21,7 +21,7 @@ package object w2d {
     container.border = border
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
+    val nonNullChildren = children
     nonNullChildren foreach { it => it.parent = container }
     container.children = nonNullChildren
     container
@@ -34,7 +34,7 @@ package object w2d {
     container.minWidth = minWidth
     container.size = Vector2(width, height)
     container.margin = Vector4(top, right, bottom, left)
-    val nonNullChildren = children.filter(it => it != null)
+    val nonNullChildren = children
     nonNullChildren foreach { it => it.parent = container }
     container.children = nonNullChildren
     container

### 2020-05-01 document/paper.tex

@@
 \usepackage{graphicx}
+\usepackage{wrapfig}
+
 % Used for displaying a sample figure. If possible, figure files should
@@
 % Shangyin
-\section{Background}
-% Shangyin
 \section{Formal problem definition}
 % Shangyin
+In program synthesis setting, 
+\section{Preliminaries}
+% Shangyin
+\subsection{Workflow}
+\begin{wrapfigure}{r}{0.25\textwidth}
+  \vspace*{-0.5in}
+  \includegraphics[width=0.25\textwidth]{src/workflow.JPG}
+\end{wrapfigure}
+We define our workflow as a two-staged program.
+In the first stage, we synthesize the input Wireframe rectangles to IR.
+Then IR is compiled into universal HTML compatible with any browser in the second stage.
+
+\subsection{IR Definition}
+
 \section{Algorithm}
 % Shangyin
-\subsection{Workflow}
-Static Graph (the absolute location of each component) $=>$ relative intermediate representation $=>$HTML
-\subsection{Grammar}
+In this section, we explain the procedures we used synthesizing the list of rectangles to IR with an estimate order of time complexity.
+We also present the compilation process from IR to final HTML result.
+\subsection{IR Synthesis}
+Recall that the input is a list of rectangles. This is the starting point of the synthesis, and we target the nested hierarchical IR. 
+\subsubsection{Cut}
+
 \subsubsection{Input}

### 2020-05-01 src/main/scala/w2d/Examples.scala
pushsss

@@ -22,26 +22,17 @@ object Examples {
       div(100, 580, top = 10, bottom = 10, left = 20, right = 20)
     ),
     // Example 3
-    vdiv(800, 1000, border = false)(
+    vdiv(800, 1020, border = false)(
       component1()
     ),
     // Example 4
-    vdiv(800, 10000, border = false)(
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
-      component1(),
+    vdiv(800, 10200, border = false)(
+      component2()
     )
   )
 
   def component1(): Container = {
-    vdiv(800, 1000, border = false)(
+    vdiv(800, 1000, border = false, top = 10, bottom = 10)(
       hdiv(800, 50, border = false)(
         div(160, 30, left = 20, right = 20, top = 10),
         div(260, 30, left = 20, right = 20, top = 10),
@@ -51,6 +42,255 @@ object Examples {
       div(400, 20, left = 200, top = 30),
       vdiv(800, 400, border = false)(
         grid(600, 400, left = 100, border = false, top = 20)(
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+        )
+      ),
+      div(780, 30, left = 10, right = 10, top = 10),
+      vdiv(800, 200, border = false)(
+        grid(720, 180, top = 10, left = 40, border = false)(
[…]

### 2020-05-02 src/main/scala/w2d/Examples.scala
testtest

@@ -22,10 +22,29 @@ object Examples {
       div(100, 580, top = 10, bottom = 10, left = 20, right = 20)
     ),
     // Example 3
+    grid(600, 400)(
+      vdiv(150, 180, border = false)(
+        div(140, 145, top = 5, left = 5, bottom = 5),
+        div(140, 20, left = 5, bottom = 5)
+      ),
+      vdiv(150, 180, border = false)(
+        div(140, 145, top = 5, left = 5, bottom = 5),
+        div(140, 20, left = 5, bottom = 5)
+      ),
+      vdiv(150, 180, border = false)(
+        div(140, 145, top = 5, left = 5, bottom = 5),
+        div(140, 20, left = 5, bottom = 5)
+      ),
+      vdiv(150, 180, border = false)(
+        div(140, 145, top = 5, left = 5, bottom = 5),
+        div(140, 20, left = 5, bottom = 5)
+      )
+    ),
+    // Example 4
     vdiv(800, 1020, border = false)(
       component1()
     ),
-    // Example 4
+    // Example 5
     vdiv(800, 10200, border = false)(
       component2()
     )
@@ -89,7 +108,7 @@ object Examples {
   }
 
   def component2(): Container = {
-    vdiv(800, 1000, border = false, top = 10, bottom = 10)(
+    vdiv(800, 100000, border = false, top = 10, bottom = 10)(
       hdiv(800, 50, border = false)(
         div(160, 30, left = 20, right = 20, top = 10),
         div(260, 30, left = 20, right = 20, top = 10),
@@ -97,8 +116,192 @@ object Examples {
       ),
       div(800, 140),
       div(400, 20, left = 200, top = 30),
-      vdiv(800, 400, border = false)(
-        grid(600, 400, left = 100, border = false, top = 20)(
+      vdiv(800, 40000, border = false)(
+        grid(600, 40000, left = 100, border = false, top = 20)(
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
+            div(140, 145, top = 5, left = 5, bottom = 5),
+            div(140, 20, left = 5, bottom = 5)
+          ),
+          vdiv(150, 180, border = false)(
[…]

### 2020-05-02 document/paper.tex

@@
 \usepackage{graphicx}
+\usepackage{float}
 \usepackage{wrapfig}
@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{color, colortbl}
+\definecolor{navy}{RGB}{0,0,205}
+\definecolor{darkred}{RGB}{178,34,34}
+\definecolor{darkblue}{RGB}{0,10,230}
+\definecolor{green}{RGB}{20,180,20}
+\definecolor{verylightgray}{RGB}{220,220,220}
+
+% colors fo rules
+\definecolor{darkgreen}{RGB}{0,153,0}
+\definecolor{darkorange}{RGB}{204,102,0}
+
+\newcommand{\dollar}{\mbox{\textdollar}}
+\definecolor{campusgold}{RGB}{194,142,14}
+\definecolor{headlinegold}{RGB}{152, 112, 13}
+\definecolor{coalgray}{RGB}{77,64,56}
+\definecolor{moongray}{RGB}{186,168,146}
+\definecolor{everblue}{RGB}{91,104,112}
+\definecolor{slayterblue}{RGB}{124,166,192}
+\definecolor{ameliablue}{RGB}{163,214,215}
+\definecolor{landgreen}{RGB}{8,92,17}
+\definecolor{rossgreen}{RGB}{132,158,42}
+\definecolor{celerygreen}{RGB}{195,190,11}
+\definecolor{springgreen}{RGB}{233,228,91}
+\definecolor{oakenbrown}{RGB}{107,69,52}
+\definecolor{bellbrick}{RGB}{199,108,20}
+\definecolor{mackeyorange}{RGB}{255,155,26}
+\definecolor{yellowwalk}{RGB}{255,209,0}
+\definecolor{fountainteal}{RGB}{46,175,155}
+\definecolor{pappyspurple}{RGB}{173,31,101}
+
+\usepackage[round]{natbib}
+\usepackage{amsmath}
+\usepackage{stmaryrd}
+\usepackage{amsfonts}
+\usepackage{listings}
+\lstdefinelanguage{Scala}%
+{morekeywords={abstract,%
+  case,catch,char,class,%
+  def,else,extends,final,finally,for,%
+  if,import,implicit,%
+  match,module,%
+  new,null,%
+  object,override,%
+  package,private,protected,public,%
+  for,public,return,super,%
+  this,%throw,throws,
+  trait,try,type,throw,%
+  val,var,%
+  with,while,%
+  yield,%
+  },%
+  sensitive,%
+  morecomment=[l]//,%
+  morecomment=[s]{/*}{*/},%
+  morestring=[b]",%
+  morestring=[b]',%
+  showstringspaces=false%
+  inputencoding=utf8,
+  extendedchars=true,
+  moredelim=[is][\overbar]{`}{`},
+  moredelim=[is][\sout]{~}{~},
+  escapechar=@
+}[keywords,comments,strings]%
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+\definecolor{violet}{rgb}{0.53, 0.0, 0.69}
+\definecolor{violet2}{rgb}{0.93, 0.51, 0.93}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstset{
+  language=Scala,
+  basicstyle=\ttfamily,
+  keywordstyle={\bfseries\color{violet}},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{blue},
+  mathescape
+}
+\usepackage[T1]{fontenc}
+\usepackage[scaled=0.9]{beramono}
 
@@
 % Shangyin
-In program synthesis setting, 
+In this work, we are given a list $L$, consisting of rectangles given their absolute coordinate with respective to origin.
+In addition, user provides the default size of the layout.
+All rectangles should be bounded by default size.
+Our objective is to find an equivalent HTML script which is:
+\begin{enumerate}
+  \item \textbf{Precise -} Render the exact same layout when opened in  default size.
+  \item \textbf{Responsive -} Automatically adjust the elements rendering if the browser is resized.
+\end{enumerate}
 \section{Preliminaries}
@@
 \subsection{Workflow}
-\begin{wrapfigure}{r}{0.25\textwidth}
-  \vspace*{-0.5in}
-  \includegraphics[width=0.25\textwidth]{src/workflow.JPG}
-\end{wrapfigure}
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  \includegraphics[width=1\textwidth]{src/workflow.JPG}
+  \caption{Workflow}
+\end{figure}
 We define our workflow as a two-staged program.
@@
 Then IR is compiled into universal HTML compatible with any browser in the second stage.
-
+\subsection{Input}
+The input is defined as a list of rectangles, given their coordinates related to $(0,0)$, the upper-left corner of the canvas.
+For the consistency, we record the coordinates of the upper-left corner of a rectangle, as well as its width and height.
 \subsection{IR Definition}
+As discussed before, the intermediate presentation captures the nested hierarchy of raw rectangles. To maintain the hierarchical structure, we defined the data structure below.
+\begin{figure}[H]
+\vspace*{-0.2in}
+\begin{lstlisting}[language=Scala,mathescape=true]
+size = <Int, Int>
+Div = <size>
+HDiv = <size, VDiv*, Grid*, Div*>
+VDiv = <size, HDiv*, Grid*, Div*>
+Grid = <size, VDiv*, HDiv*, Div*>
+Layout = Div | Grid | VDiv | HDiv
+\end{lstlisting}
+\caption{Definition of IR}
+\end{figure}
+We define \lstinline|Div| to be basic component of the hierarchy, which is equivalent to a raw rectangle in the input.
+All solid input rectangles are transformed into \lstinline|Div|s in different level of the tree in separate time during synthesizing.
+The three virtual containers for hierarchy are   \lstinline|HDiv|, \lstinline|VDiv|, \lstinline|GDiv|.
+As the name suggests, child containers of \lstinline|HDiv| and \lstinline|VDiv| are rendered in horizontal and vertical direction respectively.
+We define \lstinline|Grid| to behave like an HTML grid: two-dimensional container with auto row-wrapping.
+It contains homogenous elements, all rendered with same margin.
 

### 2020-05-02 document/paper.tex
paper

@@
 size = <Int, Int>
+margin = <Int, Int, Int, Int>
 Div = <size>
-HDiv = <size, VDiv*, Grid*, Div*>
-VDiv = <size, HDiv*, Grid*, Div*>
-Grid = <size, VDiv*, HDiv*, Div*>
+HDiv = <size, margin, VDiv*, Grid*, Div*>
+VDiv = <size, margin, HDiv*, Grid*, Div*>
+Grid = <size, margin, VDiv*, HDiv*, Div*>
 Layout = Div | Grid | VDiv | HDiv
@@
 Recall that the input is a list of rectangles. This is the starting point of the synthesis, and we target the nested hierarchical IR.
-\subsubsection{Cut}
 
-\subsubsection{Input}
-RECT\\
-RECTLIST:= RECTLIST RECT | Nil
-\subsubsection{IR}
-DIV\\
-HDIV:= HDIV|DIV|VDIV\\
-VDIV:= HDIV|DIV|VDIV\\
-First we divide the rectangles into section based on their $y$-axis. Then we use
-greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
-other rects.
+\subsubsection{Sectionalize} 
+\begin{definition}{\lstinline{section}}
+  We define a \lstinline{section} to be a set of rectangles which bounded by an inclusive lower bound $B_{low}$ and an inclusive upper bound $B_{up}$ in either $x$-direction or $y$-direction.
+In range $[B_{low}, B_{up}]$, we cannot find another bound $B_{mid}$ such that either $[B_{mid}, B_{up}]$ or $[B_{low}, B_{mid}]$ can form a \lstinline{section}.
+\end{definition}
+
+Given the list of rectangles, we divide such list into different \lstinline{section}s.
+To optimize the future operations, we want to find the max number of \lstinline{section}s.
+We propose the following sectionalize method.
+
+\begin{figure}[H]
+  \vspace*{-0.4in}
+  \begin{lstlisting}[language=Scala,mathescape=true]
+
+/*
+Input - a list $L$ of rectangle
+Output - a list $S$ of section
+*/
+
+sectionalize($L$: List[Rectangle]): List[section] = {
+  val upperBounds = $L$.map(rectangles => rectangles.getUpperBound())
+  val sectionBounds = upperBounds.filter(
+    line => doesNotCutOtherRectangle(line))
+  var $S$ = List()
+  for (sectionLine <- sectionBounds) {
+    $S$ = S + getRectangleBetween(sectionLine, lastSectionLine)
+  }
+  return $S$ 
+}
+  \end{lstlisting}
+\caption{Sectionalize}
+\end{figure}
+In the above method, we first filter all upper-bounds of rectangles that does not go through other rectangles.
+Then, we argue that these lines are the bounds of that maximize the number of \lstinline{section}s.
+The proof is trivial and omitted.
+In each \lstinline{section}, we iterate through list $L$ and find all rectangles belong to this \lstinline{section}.
+Note that no specified direction is used in the above method, so it applies to both horizontal and vertical direction: we can sectionalize $L$ based on $x$ or $y$ coordinate.
+
+Note that every \lstinline{section} can be easily converted into a \lstinline{VDiv} or \lstinline{HDiv}.
+We calculate the margin of each child rectangle of the \lstinline{section} by calculating the difference between that rectangle's coordinate and \lstinline{section} origin, which can be obtained by finding intersection of $B_{low}$ and outer coordinate.
+
+Before the sectionalize operation, every rectangle is in the same level and container: every individual rectangle will be rendered with same priority and order.
+After we sectionalize a set of rectangles, we increase the depth of the hierarchy tree by $1$.
+Now each rectangle must belong to one \lstinline{section}.
+If we view each \lstinline{section} as an individual component, there will be another virtual \textit{master} container that contains all the \lstinline{section}s, which is visualized in the following graph,
+
+\subsubsection{FormGrid} The central part of forming and optimizing the hierarchy relation is to identify \lstinline{Grid} from \lstinline{section}s.
+We see that in the previous sectionalize method, we generate a suboptimized hierarchical strucuture as we can put every rectangle into different \lstinline{VDiv} and \lstinline{HDiv} after sectionalizing.
+To further optimize the previous result, we want to merge different \lstinline{section}s into one \lstinline{Grid}.
+
+For every \lstinline{section}, we classify the \lstinline{section} into \textit{simple} and \textit{complex} lists.
+We define \textit{simple} \lstinline{section} to be the section that contains only similar rectangles and are able to form \lstinline{Grid}.
+\textit{complex} \lstinline{section} is cannot merge with other \lstinline{section} to form \lstinline{Grid} but can contain \lstinline{Grid}.
+
+Then we iterate through the list of \lstinline{section}s and enumerates all possible of combination of \lstinline{section}s.
+We group larger \lstinline{Grid} first and then process smaller ones.
+For the \lstinline{section} fail to merge with other \lstinline{section}, we put them into the \textit{complex} \lstinline{section} for future processing.
+
+% \subsubsection{Input}
+% RECT\\
+% RECTLIST:= RECTLIST RECT | Nil
+% \subsubsection{IR}
+% DIV\\
+% HDIV:= HDIV|DIV|VDIV\\
+% VDIV:= HDIV|DIV|VDIV\\
+% First we divide the rectangles into section based on their $y$-axis. Then we use
+% greedy to find the earliest possible cut $y$ such that this $y$ does not divide any
+% other rects.
 

### 2020-05-02 document/paper.tex
paper

@@
 \definecolor{darkorange}{RGB}{204,102,0}
-
+\newcommand{\W}{\textbf{W}$^2$ }
 \newcommand{\dollar}{\mbox{\textdollar}}
@@
 %
-\title{Wireframe2DOM: From Static Graph to Responsive HTML}
+\title{\W: From Static Graph to Responsive HTML}
 %
@@
 \begin{abstract}
-We propose a lightweight program synthesizer that generates HTML from static Wireframe design graph.
-With our program, a UI/UX designer with little or no programming experience can obtain responsive HTML from design layout.
-
+  We present a novel approach to synthesize and generate a nested and responsive UI layout from a wireframe, a common tool used by UI/UX designers to draft their design of a client application.
+Given the wireframe design of an application's layout in absolute coordinates, \W synthesizes an HTML file that when rendered by any modern browser, not only places the components in their original positions, but also automatically adapts to changes in the viewer's screen size using modern HTML and CSS techniques.
+Furthermore, the resulting HTML has a clearly defined parent-child hierarchy, enabling the application developer to iterate and detail it quickly.
+Preliminary benchmark results show that W2 is able to synthesize an absolute wireframe layout consisting of 200+ rectangles into an HTML hierarchy tree of depth 5 in under 2ms.
 \keywords{Program Synthesis  \and Web Development \and User Interface}
@@
 \section{Introduction}
-Program synthesis community targets mainly on string processing and integer manipulating problem.
-However, the need for generating web application and other Graphical User Interface(GUI) applications is growing.
-While some UI/UX designers are capable of writing frontend code, providing them with a tool that generating HTML code can be beneficial.
-With HTML code equivalent to their interface design, designers can edit, test, and improve the original static layout.
-For example, many web applications now seek compatibility between PC and mobile devices.
-The different sizes complicate the designers' work.
-Some layouts are more promising on $16:9$ screen than on other smart devices.
-With the responsive HTML generated by our project, designer can preview the layout in a new resolution without re-drawing.
+UI/UX design plays an important role in most software applications.
+It allows software users to interact with the software functions and perform the designated tasks in an intuitive and effective way.
+The usual client application development cycle is as below: the UI/UX designer first designs the application layout, then provides it in image format to the application developer, who then writes code that when rendered resembles the design.
+However, the latter task is often time-consuming and error-prone.
+For instance, the spacings between the layout elements, referred to as margins, are often not accurately implemented by the application programmer, either because they are not explicitly stated in the design or such process simply takes too much time, so that the programmer uses estimated values instead.
 
-Our work focuses on configure the relationship between each atom elements in the static layout.
-We combine components of different sizes and locations into horizontal/vertical divisions and grids.
-Instead of the absolute coordinate given by input, we assign margin to the converted structure and remember the relative position between them.
-Without the limitation of absolute coordinates, the converted structures can be rendered with the designers' true intention.
+Furthermore, as the popularity of mobile devices grows, a single fixed layout is no longer sufficient.
+In the context of web application development, most websites today use a responsive layout, which refers to a flexible, fluid layout that resizes itself to fit the size of the viewer's display.
+For instance, consider the layout of YouTube (Figure 1a and 1b), a popular video website.
+When the viewer is using a desktop computer whose resolution width is higher than a threshold in pixels, the website shows the videos in 4 columns; when the viewer is using a mobile device with a much smaller width in pixels, however, the website shows the videos in 2 columns.
+To achieve this result, both the UI/UX designer and the application programmer have to do extra amount of work: the UI/UX designer must design multiple versions of the layout in different screen sizes, and the application programmer must write code that incorporates these layouts such that it renders correctly across all supported screen sizes.
+Specifically, the application programmer has to work out the parent-child relationships between the elements, known as the layout hierarchy.
+Unfortunately, this task is also time-consuming and error-prone, as the layout relationships are not immediately clear.
+For example, Figure 2 shows a simplified layout hierarchy of YouTube when rendered on a mobile device, in which the innermost element has a depth of 5.
+Along with even more complicated margins, this task poses a considerable challenge to the application programmer.
+\paragraph{Our Work} In this paper, we present a proof-of-concept framework, named \W (Synthesizing responsive Webpage from Wireframe), to address the stated challenges.
+Specifically, we present the following technical contributions:
+\W introduces a fast sectionalization algorithm to synthesize any absolute layout with hundreds of elements, specified by their absolute screen coordinates (x and y) and sizes (width and height), into a nested layout with hierarchical information inferred under a few milliseconds.
+\W introduces a direct mapping of nested layouts to an HTML DOM (Document Object Model), exploiting the latest HTML5 features: flexboxes and grids.
+The resulting HTML can be rendered by any modern browser on its compatible devices.
 
 \section{Related work}
+There has been similar research in the area of generating layout code from images/rectangles.
+However; we did not find any work that comes too close to \textbf{W}$^2$: there is a machine-learning based approach to generate a web page from a mockup image [Huang et al.
+2016], but it does not have a hierarchical layout specification; another approach aims to synthesize a relational layout\protect\footnote{ Note that "relational layout" is not the same as "hierarchical layout." In their work, the term "relational" refers to how the elements are relatively positioned against each other, i.e.
+the inter-element spacings.} for Android applications from a set of rectangles [Bielik et al.
+2018], but it produces a flat hierarchy that relies on ConstraintLayout, a newly introduced feature in the newer versions of Android SDK, which is not as portable as HTML5 which is universal and cross-platform.
+
+There is also work on generating UI layout for alternative screen orientation [Zeidler et al.
+2017] and vectorizing UI screenshots [Swearngin et al.
+2018]; but, once again, they did not target the web platform like \textbf{W}$^2$, which leverages HTML5 features to enable the resulting layout's responsiveness.
+
 % Tiger
@@
 \section{Illustrative example}
-% Shangyin
+There is a significant difference in mobile website and desktop website layout due to various screen width between end-devices. 
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  %\includegraphics[width=1\textwidth]{src/youtube.JPG}
+  \caption{Different Rendering in Mobile and PC}
+\end{figure}
+The above shows an example of different rendering of the same website.
+When the UI/UX designer design a static wireframe layout, it only applies to one specific layout without generality.
+Our work takes the advantage of the responsiveness of HTML components and infer the HTML's hierarchical structure from the given static wireframe.
+
 \section{Formal problem definition}
@@
 We define \textit{simple} \lstinline{section} to be the section that contains only similar rectangles and are able to form \lstinline{Grid}.
-\textit{complex} \lstinline{section} is cannot merge with other \lstinline{section} to form \lstinline{Grid} but can contain \lstinline{Grid}.
+\textit{Complex} \lstinline{section} is cannot merge with other \lstinline{section} to form \lstinline{Grid} but can contain \lstinline{Grid}.
+% \begin{figure}[H]
+%   \vspace*{-0.1in}
+%   \includegraphics[width=1\textwidth]{src/simplevscomplex.JPG}
+%   \caption{Workflow}
+% \end{figure}
 
@@
 For the \lstinline{section} fail to merge with other \lstinline{section}, we put them into the \textit{complex} \lstinline{section} for future processing.
+
+\subsubsection{Complex Section}
+\textit{Complex} \lstinline{section} indicates the need for further processing.
+The nature of web-page rendering suggests that elements are either arranged horizontally or vertically.
+Therefore, if the \textit{complex} \lstinline{section} was sectionalized based on $x$-coordinate, we now sectionalize it based on $y$-coordinate and vice versa.
+Within each \textit{complex} \lstinline{section}, we perform the above sectionalize and formGrid operation recursively until we meet max-depth or a single \lstinline{Div}.
+
+In each execution of sectionalize and formGrid operation, we increase the depth of the hierarchy tree by 1. The result tree after termination is the IR we get and then feed into the IR-HTML compiler.
+There are rare cases where the hierarchy tree produced fail to be optimal layout. We will discuss in future sections.
 

### 2020-05-02 document/paper.tex
paper

@@
 In the context of web application development, most websites today use a responsive layout, which refers to a flexible, fluid layout that resizes itself to fit the size of the viewer's display.
-For instance, consider the layout of YouTube (Figure 1a and 1b), a popular video website.
+For instance, consider the layout of YouTube [Figure 1], a popular video website.
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  \includegraphics[width=1\textwidth]{src/youtube.JPG}
+  \caption{Difference in Youtube Layout}
+\end{figure}
 When the viewer is using a desktop computer whose resolution width is higher than a threshold in pixels, the website shows the videos in 4 columns; when the viewer is using a mobile device with a much smaller width in pixels, however, the website shows the videos in 2 columns.
@@
 \section{Illustrative example}
-There is a significant difference in mobile website and desktop website layout due to various screen width between end-devices. 
+When the wireframe is designed, we are given a static layout graph [Figure 2].
 \begin{figure}[H]
   \vspace*{-0.1in}
-  %\includegraphics[width=1\textwidth]{src/youtube.JPG}
-  \caption{Different Rendering in Mobile and PC}
+  \includegraphics[width=0.5\textwidth]{src/compare.JPG}
+  \caption{Static Wireframe Graph}
 \end{figure}
-The above shows an example of different rendering of the same website.
-When the UI/UX designer design a static wireframe layout, it only applies to one specific layout without generality.
-Our work takes the advantage of the responsiveness of HTML components and infer the HTML's hierarchical structure from the given static wireframe.
+We aim to transform this static layout to HTML script can directly run in browser.
+With our inference of the hierarchical structure, the website rendered by HTML can adjust and adapt to various width [Figure 3]
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  \includegraphics[width=1\textwidth]{src/compare.JPG}
+  \caption{Responsive in Different Width}
+\end{figure}
 

### 2020-05-02 document/paper.tex
paper

@@
   \vspace*{-0.1in}
-  \includegraphics[width=1\textwidth]{src/youtube.JPG}
+  \includegraphics[width=1\textwidth]{src/youtube.jpg}
   \caption{Difference in Youtube Layout}
@@
   \vspace*{-0.1in}
-  \includegraphics[width=0.5\textwidth]{src/compare.JPG}
+  \includegraphics[width=0.5\textwidth]{src/wireframe.JPG}
   \caption{Static Wireframe Graph}
@@
 We aim to transform this static layout to HTML script can directly run in browser.
-With our inference of the hierarchical structure, the website rendered by HTML can adjust and adapt to various width [Figure 3]
+With the inference of the hierarchical structure by \textbf{W}$^2$, the website generated can adjust and adapt to various width [Figure 3]
 \begin{figure}[H]
   \vspace*{-0.1in}
-  \includegraphics[width=1\textwidth]{src/compare.JPG}
+  \includegraphics[width=1\textwidth]{src/compare.jpg}
   \caption{Responsive in Different Width}
@@
 \section{Evaluation}
-% Tiger
+We ran \W on a small set of representative test cases (|s|=5).
+Test case 1 to 3 are simple layouts; test case 4 is a design that is close to that in a real-world scenario (most rectangles are irregularly aligned, multiple layers of depth), and test case 5 is for stress testing (> 200 rectangles).
+The results are as below:
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  \includegraphics[width=1\textwidth]{src/benchmark.JPG}
+  \caption{Benchmark}
+\end{figure}
+As our algorithm has a very limited search space and most UI layouts have fewer than 100 elements, it runs extremely fast—much faster than most similar work.
+Also, unlike neural-network based methods that often generate code that is non-interpretable or syntactically incorrect, \W produces a clean and robust DOM tree that is ready for display in the browser and easy to modify.
+
+However, there are some limitations with \textbf{W}$^2$.
+For example, for a layout shown in Figure X, there exists two possible ways to sectionalize the layout, and \W always chooses the latter, due to its nature of returning the hierarchical tree of maximized depth.
+In the practical sense, though, the former sectionalization is more common as most websites adapt a multi-column layout.
+We have yet to clearly define a user-customizable parameter to measure the optimality of our synthesized hierarchy; hence, the resulting layout may not match the user's intent.
+\begin{figure}[H]
+  \vspace*{-0.1in}
+  \includegraphics[width=1\textwidth]{src/limit.JPG}
+  \caption{Benchmark}
+\end{figure}
+
 \section{Conclusion}
